Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-16 main.tex
:pencil: Add quick one-side proof

			To explicitly specify the instances of the backscatter symbols, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \in \mathcal{M} : k \in \mathcal{K}\}$ and label the corresponding tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} \in \mathcal{C} : m_k \in \mathcal{M}, k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and \gls{awgn} $w[n]$, and thus follows \gls{cscg} distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$. For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

@@

			On top of this, we can compute the marginal probability of each tag and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}. The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus \{k\}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

@@

			We first introduce some prerequisites of information theory. Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(\bar{c}_1),\ldots,P_k(\bar{c}_M)]^T \in \mathbb{R}^{M \times 1}$, $\boldsymbol{P} \triangleq [\boldsymbol{p}_1^T,\ldots,\boldsymbol{p}_K^T]^T \in \mathbb{R}^{M \times K}$. Assume the input distribution of all tags are mutually independent such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the backscatter information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as

@@

				I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),

@@

@@

			and the backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}

@@

					& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate_expansion}

@@

		\begin{subsection}{Ergodic primary rate}
			Once the tag input combination is successfully decoded, the user can eliminate backscatter uncertainty and model its contribution within the equivalent primary channel \eqref{eq:equivalent_primary_channel}. As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $q$ associated with symbol $\bar{c}_{i_q}$ respectively as
			\begin{align}
				I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})
				& \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),\label{eq:primary_information_function}\\
				I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y})
				& \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_{k}(\bar{c}_{m_{k}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
			\end{align}
			% \begin{equation}
			% 	I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			% \begin{equation}
			% 	I_{\mathrm{P},k}(\bar{c}_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			% \begin{equation}
			% 	I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}}) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			and the ergodic primary rate can be expressed as\footnote{The unit of \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}--\eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
			\begin{subequations}
				\begin{align}
					I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y})
					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y})\right]\label{eq:primary_ergodic_rate_expectation}\\
					& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
					\label{eq:primary_ergodic_rate_expansion}
				\end{align}
				\label{eq:primary_ergodic_rate}
			\end{subequations}
			% \begin{align}
			% 	I_{\mathrm{P}}(c_{\mathcal{K}})
			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}})\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})\right]\\
			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			% 	\label{eq:primary_ergodic_rate}
			% \end{align}

@@

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary-backscatter rate region}
			The weighted sum marginal information of tag $q$ associated with symbol $\bar{c}_{i_q}$ and the weighted sum primary-backscatter rate are defined respectively as
			\begin{align}
				I_q(\bar{c}_{i_q};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{i_q};z),\label{eq:weighted_sum_marginal_information}\\
				I(c_{\mathcal{K}};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),\label{eq:weighted_sum_rate}
			\end{align}
			where $\rho \in [0,1]$ denotes the priority of the primary link. To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum primary-backscatter rate
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
			\end{maxi!}
			where \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} are input probability constraints and \eqref{co:average_transmit_power} is the average transmit power budget. As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P}}}{I}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are necessary and sufficient for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}
			\begin{proposition}
				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
				\begin{subequations}
					\begin{alignat}{2}
						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\label{co:probable_states}\\
						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.\label{co:dropped_states}
					\end{alignat}
				\end{subequations}

				% \eqref{co:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{co:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
				An interpretation is that each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while any state of any tag with potentially less marginal information than above should not be used.
				% \begin{itemize}
				% 	\item each probable state of each tag produces the same marginal information (averaged over all states of other tags)
				% 	\item all states of all tags with potentially less marginal information should be dropped
				% \end{itemize}
				% An input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information. Specifically, the optimal $\boldsymbol{P}^{\star}$ to problem~\eqref{op:input_probability_distribution}

>>>>

			To explicitly specify the instances of the backscatter symbols, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \in \mathcal{M} : k \in \mathcal{K}\}$ and label the corresponding tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} \in \mathcal{C} : m_k \in \mathcal{M}, k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and \gls{awgn} $w[n]$, and thus follows \gls{cscg} distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$. For the ease of exposition, we denote the hypothesis that the tag input combination at state $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

@@

			On top of this, we can compute the marginal probability of each tag and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}. The probability of observing energy level $j$ when tag $k$ at state $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus \{k\}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

@@

			We first introduce some prerequisites of information theory. Define the input probability distribution of tag $k$ at state $m_k$ as $P_k(\bar{c}_{m_k})$, and let $\boldsymbol{p}_k \triangleq [P_k(\bar{c}_1),\ldots,P_k(\bar{c}_M)]^T \in \mathbb{R}^{M \times 1}$, $\boldsymbol{P} \triangleq [\boldsymbol{p}_1^T,\ldots,\boldsymbol{p}_K^T]^T \in \mathbb{R}^{M \times K}$. Assume the input distribution of all tags are mutually independent such that the probability associated with input combination $\bar{c}_{m_{\mathcal{K}}}$ satisfies $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the corresponding backscatter information function is defined as

@@

				I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),

@@

			% 	I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),

@@

			where $P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) = \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k})$. The backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}

@@

					& = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate_expansion}

@@

		\begin{subsection}{Ergodic primary rate}
			Once the tag input combination is successfully decoded, the user can eliminate backscatter uncertainty and model its contribution within the equivalent primary channel \eqref{eq:equivalent_primary_channel}. As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $q$ associated with symbol $\bar{c}_{i_q}$ respectively as
			\begin{align}
				I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})
				& \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),\label{eq:primary_information_function}\\
				I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y})
				& \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} P_{\mathcal{K} \setminus \{q\}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
			\end{align}
			% \begin{equation}
			% 	I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			% \begin{equation}
			% 	I_{\mathrm{P},k}(\bar{c}_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			% \begin{equation}
			% 	I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}}) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			and the ergodic primary rate can be expressed as\footnote{The unit of \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}--\eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
			\begin{subequations}
				\begin{align}
					I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y})
					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y})\right]\label{eq:primary_ergodic_rate_expectation}\\
					& = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
					\label{eq:primary_ergodic_rate_expansion}
				\end{align}
				\label{eq:primary_ergodic_rate}
			\end{subequations}
			% \begin{align}
			% 	I_{\mathrm{P}}(c_{\mathcal{K}})
			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}})\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})\right]\\
			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			% 	\label{eq:primary_ergodic_rate}
			% \end{align}

@@

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary-backscatter rate region}
			The weighted sum marginal information of tag $q$ associated with symbol $\bar{c}_{i_q}$ and the weighted sum primary-backscatter rate are defined respectively as
			\begin{align}
				I_q(\bar{c}_{i_q};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{i_q};z),\label{eq:weighted_sum_marginal_information}\\
				I(c_{\mathcal{K}};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),\label{eq:weighted_sum_rate}
			\end{align}
			where $\rho \in [0,1]$ denotes the priority of the primary link. To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum primary-backscatter rate
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
			\end{maxi!}
			where \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} are input probability constraints and \eqref{co:average_transmit_power} is the average transmit power budget. As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are necessary and sufficient for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}
			\begin{proposition}
				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
				\begin{subequations}
					\begin{alignat}{2}
						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\label{co:probable_states}\\
						I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.\label{co:dropped_states}
					\end{alignat}
				\end{subequations}

				\eqref{co:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{co:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
				% An interpretation is that each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while any state of any tag with potentially less marginal information than above should not be used.
				% \begin{itemize}
				% 	\item each probable state of each tag produces the same marginal information (averaged over all states of other tags)
				% 	\item all states of all tags with potentially less marginal information should be dropped
				% \end{itemize}
				% An input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information. Specifically, the optimal $\boldsymbol{P}^{\star}$ to problem~\eqref{op:input_probability_distribution}
